---
title: "CSDS313 - Homework2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Including Code
You can include R code in the document as follows:

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(rvest)
```
```{r}
movie_votes <- read.csv("movie_votes.csv")
airport_routes <- read.csv('airport_routes.csv')
```
```{r}
head(movie_votes, 10)
```
```{r}
head(airport_routes, 10)
```
```
#Airports data 

```{r}
#power 
airdata =airport_routes$NumberOfRoutes
x_min <- min(airdata[airdata > 0]) 
a = 1 + length(airdata)/(sum(airdata/x_min))
print(a)
```

```{r}
#exponential 
airdata =airport_routes$NumberOfRoutes
lambda = length(airdata)/sum(airdata)
print(lambda)
```
 
```{r}
#uniform 
airdata =airport_routes$NumberOfRoutes
a = min(airdata)
b = max(airdata)
print(a)
print(b)
```

```{r}
#normal 
airdata =airport_routes$NumberOfRoutes
mu = sum(airdata)/length(airdata)
sigmaval = sqrt(sum((airdata-mu)**2)/length(airdata))
print(mu)
print(sigmaval)
```

#Plotting emperical data and function generated data 

#Moviedata 
```{r}
#power 
movdata =movie_votes$AverageVote
x_min <- min(movdata[movdata > 0]) 
a = 1 + length(movdata)/(sum(movdata/x_min))
print(a)
```

```{r}
#exponential 
movdata =movie_votes$AverageVote
lambda = length(movdata)/sum(movdata)
print(lambda)
```

```{r}
#uniform 
movdata =movie_votes$AverageVote
a = min(movdata)
b = max(movdata)
print(a)
print(b)
```

```{r}
#normal 
movdata =movie_votes$AverageVote
mu = sum(movdata)/length(movdata)
sigmaval = sqrt(sum((movdata-mu)**2)/length(movdata))
print(mu)
print(sigmaval)
```

```{r}
# Load required packages
library(ggplot2)
library(gridExtra)

# Sample size
movdata =movie_votes$AverageVote
n <- length(movdata)

# Generate empirical data (e.g., random data)
empirical_data <- movdata

# Generate synthetic data for different distributions
power_data <- rpower(n, alpha = 1.3)
exponential_data <- rexp(n, rate = 0.161)
uniform_data <- runif(n, min = 1.9, max = 8.5)
normal_data <- rnorm(n, mean = 6.227, sd = 0.893)

# Create separate density plots for each distribution
plot_empirical <- ggplot(data.frame(x = empirical_data), aes(x)) +
  geom_density(fill = "blue", alpha = 0.5) +
  labs(title = "Empirical Data") +
  theme(
    plot.title = element_text(size = 20),  # Adjust the plot title font size
    axis.title = element_text(size = 18),   # Adjust the axis label font size
    legend.text = element_text(size = 16),  # Adjust the legend item font size
    axis.text = element_text(size = 16)  # Adjust the axis tick font size
  )

plot_power <- ggplot(data.frame(x = power_data), aes(x)) +
  geom_density(fill = "green", alpha = 0.5) +
  labs(title = "Power Distribution") +
  theme(
    plot.title = element_text(size = 20),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    axis.text = element_text(size = 16)
  )

plot_exponential <- ggplot(data.frame(x = exponential_data), aes(x)) +
  geom_density(fill = "red", alpha = 0.5) +
  labs(title = "Exponential Distribution") +
  theme(
    plot.title = element_text(size = 20),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    axis.text = element_text(size = 16)
  )

plot_uniform <- ggplot(data.frame(x = uniform_data), aes(x)) +
  geom_density(fill = "purple", alpha = 0.5) +
  labs(title = "Uniform Distribution") +
  theme(
    plot.title = element_text(size = 20),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    axis.text = element_text(size = 16)
  )

plot_normal <- ggplot(data.frame(x = normal_data), aes(x)) +
  geom_density(fill = "orange", alpha = 0.5) +
  labs(title = "Normal Distribution") +
  theme(
    plot.title = element_text(size = 20),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    axis.text = element_text(size = 16)
  )


# Print each plot individually
ggsave("empirical_plot_movie.png", plot = plot_empirical, width = 10, height = 8, dpi = 300)
ggsave("power_distribution_plot_movie.png", plot = plot_power, width = 10, height = 8, dpi = 300)
ggsave("exponential_distribution_plot_movie.png", plot = plot_exponential, width = 10, height = 8, dpi = 300)
ggsave("uniform_distribution_plot_movie.png", plot = plot_uniform, width = 10, height = 8, dpi = 300)
ggsave("normal_distribution_plot_movie.png", plot = plot_normal, width = 10, height = 8, dpi = 300)
```

```{r}
# Load required packages
library(ggplot2)
library(gridExtra)

# Sample size
airdata =airport_routes$NumberOfRoutes
n <- length(airdata)

# Generate empirical data (e.g., random data)
empirical_data <- airdata

# Generate synthetic data for different distributions
power_data <- rpower(n, alpha = 1.05)
exponential_data <- rexp(n, rate = 0.05)
uniform_data <- runif(n, min = 1, max = 915)
normal_data <- rnorm(n, mean = 19.845, sd = 53.499)

# Create separate density plots for each distribution
plot_empirical <- ggplot(data.frame(x = empirical_data), aes(x)) +
  geom_density(fill = "blue", alpha = 0.5) +
  labs(title = "Empirical Data") +
  theme(
    plot.title = element_text(size = 20),  # Adjust the plot title font size
    axis.title = element_text(size = 18),   # Adjust the axis label font size
    legend.text = element_text(size = 16),  # Adjust the legend item font size
    axis.text = element_text(size = 16)  # Adjust the axis tick font size
  )

plot_power <- ggplot(data.frame(x = power_data), aes(x)) +
  geom_density(fill = "green", alpha = 0.5) +
  labs(title = "Power Distribution") +
  theme(
    plot.title = element_text(size = 20),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    axis.text = element_text(size = 16)
  )

plot_exponential <- ggplot(data.frame(x = exponential_data), aes(x)) +
  geom_density(fill = "red", alpha = 0.5) +
  labs(title = "Exponential Distribution") +
  theme(
    plot.title = element_text(size = 20),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    axis.text = element_text(size = 16)
  )

plot_uniform <- ggplot(data.frame(x = uniform_data), aes(x)) +
  geom_density(fill = "purple", alpha = 0.5) +
  labs(title = "Uniform Distribution") +
  theme(
    plot.title = element_text(size = 20),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    axis.text = element_text(size = 16)
  )

plot_normal <- ggplot(data.frame(x = normal_data), aes(x)) +
  geom_density(fill = "orange", alpha = 0.5) +
  labs(title = "Normal Distribution") +
  theme(
    plot.title = element_text(size = 20),
    axis.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    axis.text = element_text(size = 16)
  )


# Print each plot individually
ggsave("empirical_plot_airport.png", plot = plot_empirical, width = 10, height = 8, dpi = 300)
ggsave("power_distribution_plot_airport.png", plot = plot_power, width = 10, height = 8, dpi = 300)
ggsave("exponential_distribution_plot_airport.png", plot = plot_exponential, width = 10, height = 8, dpi = 300)
ggsave("uniform_distribution_plot_airport.png", plot = plot_uniform, width = 10, height = 8, dpi = 300)
ggsave("normal_distribution_plot_airport.png", plot = plot_normal, width = 10, height = 8, dpi = 300)
```
